\documentclass{article}
\usepackage{hyperref}
\usepackage[left=3cm,top=3cm,right=3cm,nohead,bottom=3cm]{geometry}
\title{15-414 Bug Catching: \mbox{Automated Program Verification and Testing}}
\date{Monday/Wednesday 3:00 - 4:20, GHC 4211\\
  \url{http://www.cs.cmu.edu/~emc/15414-f11}
}
\author{Edmund Clarke \and Sagar Chaki 
  \and Arie Gurfinkel
}
\begin{document}
\maketitle
\section{Course Description}
At some point in their careers, most CS and ECE students will develop
software or hardware that must be ultra reliable. Logical errors in
such designs can be costly, even life threatening. There has already
been a number of well publicized errors like the Intel Pentium
floating point error and the Ariane 5 crash. In this course we will
study foundational concepts, and tools built on them, for finding and
preventing such errors. We will cover some of the most prominent ideas
in this important and evolving field -- including propositional
satisfiability, Binary Decision Diagrams, model checking, abstraction,
static analysis, abstraction-refinement, bounded model checking, and
probabilistic model checking. We will also study some of the
successful tools in this area. There will be emphasis on both the
theoretical basis of these tools, as well as their hands-on use on
real examples. This course can be used as one of the Fundamentals of
Algorithms requirement.

Following is the list of topics that we intend to cover in the
course. The emphasis of the course is on effective use of verification
tools. We hope that at the end of the course, students will be able to
do research in this area.
\begin{itemize}
\item Overview of model checking
\item Quick introduction to logic
  \begin{itemize}
  \item Propositional logic
  \item Davis Putnam procedure, fast SAT solvers
  \end{itemize}
\item Binary Decision Diagrams (BDDs)
\item Property specification using Computation Tree Logic (CTL)
\item Linear Temporal Logic (LTL)
\item LTL tableaux construction
\item LTL model checking
\item Explicit state model checking
\item Partial order reduction
\item Symbolic model checking
\item Detailed introduction to model checker SMV
\item Detailed introduction to model checker SPIN
\item Abstract interpretation
\item Predicate abstraction and abstract refinement
\item Detailed introduction to model checker CBMC
\item Compositional model checking
\item Probabilistic model checking
\item Statistical model checking
\end{itemize}

\section{Textbook}
\begin{itemize}
\item Edmund M. Clarke Jr., Orna Grumberg, and Doron A. Peled, ``Model Checking''
\item Mordechai Ben-Ari, ``Principles of the Spin Model Checker''
\end{itemize}

\section{Grading and Policies}
\subsection{Grading}
Grading will be based on class participation, assignments, a midterm,
and a final project. The assignments are worth 30\% of the final
grade, midterm exam is worth 30\% of the final grade, final project is
worth 35\% of the final grade, and class participation is worth 5\% of
the final grade.

\subsection{Homeworks}
\begin{itemize}
\item There will be a problem set about every two weeks.
\item All homeworks are due at the beginning of class.
\item All homeworks must be either typed, preferably in LaTeX, or
  legible if it's paper copy.
\item We will not accept late submission.
\item You are welcome to confer with other students on homeworks, just
  don't turn in the exact same solution. You have to prepare the
  solution individually.
\item At the top of your assignment, write down whom you worked with,
  if anyone.
\end{itemize}

\subsection{Project}
Projects should be done in groups of two.

\subsection{Cheating}
It can be surprisingly easy to detect when students are not doing
their own work. Working with others on the assignments does not mean
dividing the problems among you, and then swapping answers.

\section{Contact Information}
\subsection{Instructors}
\begin{itemize}
\item Prof. Edmund M. Clarke
  \begin{itemize}
  \item \url{emc@cs.cmu.edu}
  \item Office: GHC 9231 
  \item Phone: (412) 268-2628 
  \item Office hours: By appointment
  \end{itemize}
\item Dr. Sagar Chaki 
  \begin{itemize}
  \item \url{chaki@sei.cmu.edu}
  \item Office: SEI 
  \item Phone: (412) 268-1436 
  \item Office hours: By appointment
  \end{itemize}
\item Dr. Arie Gurfinkel 
  \begin{itemize}
  \item \url{arie@cmu.edu}
  \item Office: SEI 
  \item Phone: (412) 268-7788 
  \item Office hours: By appointment
  \end{itemize}
\end{itemize}

\subsection{Teaching Assistants}
\begin{itemize}
\item Soonho Kong
  \begin{itemize}
  \item \url{cmu15414ta@gmail.com}
  \item Office: GHC 7609 
  \item Phone: 412-268-3076 
  \item Office hours: By appointment
  \end{itemize}
\item David Henriques 
  \begin{itemize}
  \item \url{cmu15414ta@gmail.com}
  \item Office: GHC 7511 
  \item Phone: 412-268-2582 
  \item Office hours: By appointment	
  \end{itemize}
\end{itemize}

\subsection{Course Secretary}
\begin{itemize}
\item Denny Marous 
  \begin{itemize}
  \item \url{dcm@cs.cmu.edu}
  \item Office: GHC 9229 
  \item Phone: 412-268-7660
  \end{itemize}
\end{itemize}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
